---
title: "Assignment"
author: "Callie Stephenson"
date: "2023-08-17"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
########## Load Libraries 
# Load packages raster, habtools, ggplot2, dplyr, fishualize
library(raster)
library(habtools)
library(ggplot2)
library(dplyr)
library(fishualize)

#### test that habtools loaded appropriately
plot(horseshoe)
```

### Current lab 
Donahue Lab

### Project focus 
Thesis work is on effects of submarine groundwater discharge (a natural environmental gradient) on coral reef ecosystem functioning. Specifically looking at fish community structure and coral growth / health.

### Why you chose this course 
I believe furthering my understanding of how structure relates to ecosystem functioning will enhance my ability to ask scientific questions related to the topics. This subject matter relates to my current projects and long-term career goals. 

### What do you want to learn about the most in this course
The techniques commonly used to test and analyze questions related to ecosystem functioning vs. the ecosystem's structure.

### Your R experience
Light, have taken MBIO 612 (Data Science Fundamentals in R) and can get by, but I get by with a little help from my friends.

### Fun fact 
I do a back handspring every six months to make sure I still can (I still can)
